Capitalized Title Here

### 2021-03-31 CMPSpaper_writing/CMPSpaper_writing.Rmd
small edits

The CMPS algorithm consists of \hh{three main} steps:

1. **cut the reference profile into consecutive, non-overlapping and equal-length basis segments:**
the command `get_segs(x, len=50)` implements this first step. 
It takes a profile {XXX profile or signature?} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.

@@

@@

`get_ccf4` computes the cross-correlation function / correlation coefficient curve between two profiles. This is the function called whenever we need to compute the ccf.

@@

`get_seg_scale` takes a basis segment and increases its segment length. `scale=1` gives the original length of the basis segment. Increasing `scale` by 1 will double the segment length.

`get_ccr_peaks` takes a segment and the comparison profile, then computes the correlation coefficient curve between them and finds peaks on the correlation coefficient curve. The number of peaks detected is equal to `npeaks`. And we are using `rollapply` to find peaks on the curve effectively.

`get_ccp` checks if the "consistent correlation peak" exists under the framework of multi segment lengths strategy. Since we are requiring the highest segment scale identifies only one peak, we just need to check if this peak shows any "consistency". In other words, we check if this peak is also identified as a peak in other segment scales.

step 3) determine the congruent registration position with a small tolerance zone and the number of basis segments that take the congruent registration position as their "best" registration position. These segments are called the "congruent matching profile segments" (CMPS), and the number of CMPS is the CMPS score of this profile comparison.

`get_CMPS` considers all basis segments and their identified peak positions to determine the congruent registration position. The goal is to find a peak position that is agreed by the most basis segments. Since small errors are allowed, a tolerance zone would serve as a selection window. `get_CMPS` will move this selection window from left to right and go through all possible positions and check the number of basis segment that identifies a peak in the selection window for each position. Since we are moving this tolerance zone from left to right one unit a time, some consecutive positions are expected to have the same number of basis segments. [?.?]In that case the median of all tied and consecutive positions will be chosen as the congruent registration position. As long as the congruent registration position is determined, the number of basis segments that identify a peak in this position is the CMPS score.

>>>>

Conceptually, the CMPS algorithm consists of \hh{three main} steps:

1. **cut the reference profile into consecutive, non-overlapping and equal-length basis segments:**

@@

3. **determine the congruent registration position** with a small tolerance zone and the number of basis segments that take the congruent registration position as their "best" registration position. These segments are called the "congruent matching profile segments" (CMPS), and the number of CMPS is the CMPS score of this profile comparison.

@@

\hh{In the CMPS package, these three steps are implemented using a set of key functions:}

* The command `get_segs(x, len=50)` implements step 1:  It takes a profile {XXX profile or signature?} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.

* `get_ccf4` computes the cross-correlation function / correlation coefficient curve between two profiles. This is the function called whenever we need to compute the ccf.

@@

* `get_seg_scale` takes a basis segment and increases its segment length. `scale=1` gives the original length of the basis segment. Increasing `scale` by 1 will double the segment length.

* `get_ccr_peaks` takes a segment and the comparison profile, then computes the correlation coefficient curve between them and finds peaks on the correlation coefficient curve. The number of peaks detected is equal to `npeaks`. And we are using `rollapply` to find peaks on the curve effectively.

* `get_ccp` checks if the "consistent correlation peak" exists under the framework of multi segment lengths strategy. Since we are requiring the highest segment scale identifies only one peak, we just need to check if this peak shows any "consistency". In other words, we check if this peak is also identified as a peak in other segment scales.

* `get_CMPS` considers all basis segments and their identified peak positions to determine the congruent registration position. The goal is to find a peak position that is agreed by the most basis segments. Since small errors are allowed, a tolerance zone would serve as a selection window. `get_CMPS` will move this selection window from left to right and go through all possible positions and check the number of basis segment that identifies a peak in the selection window for each position. Since we are moving this tolerance zone from left to right one unit a time, some consecutive positions are expected to have the same number of basis segments. [?.?]In that case the median of all tied and consecutive positions will be chosen as the congruent registration position. As long as the congruent registration position is determined, the number of basis segments that identify a peak in this position is the CMPS score.
